RSA_model2

### 2015-10-28 models/RSA_Model2.Rmd
minor tweaks for symsys preso 10.26.15

Run model
---------
```{r}
alpha = 4
md <- data %>%
  do(run.rsa(., alpha = alpha, useprior = T, usenone = T))
```

@@

Tuning
-------
```{r}
# alpha
alphas = seq(from=1, to=10)
fit = sapply(alphas, FUN=function(n) {
  md <- data %>%
    do(run.rsa(., alpha = n, useprior = F, usenone = T))

>>>>

Run model
---------
```{r}
alpha = 5
md <- data %>%
  do(run.rsa(., alpha = alpha, useprior = T, usenone = F))
```

@@

Tuning
-------
```{r}
# alpha
alphas = seq(from=1, to=10)
fit = sapply(alphas, FUN=function(n) {
  md <- data %>%
    do(run.rsa(., alpha = n, useprior = F, usenone = F))
